Examples Aided Synthesis Examination

### 2020-03-20 intro.tex
Oops, I rewrote the intro

\section{Introduction}

Imagine asking your computer to write a function for you and it works on the
first try.
%
Well, program synthesis isn't quite there.
%
But getting there will necessarily involve some back and forth between the user
and computer.
%
Often the function specification is less precise the than function requested.
%
In this case, a program synthesizer can come up with any number of solutions
that all meet the specification, to varying degrees of utility.

Our work is based on \hoogleplus, a program synthesis engine for the
Haskell programming language \cite{hoogle_plus_2020}.
%
A user inputs a type signature of a function, like \texttt{a -> [Maybe a] -> a}
(read: ``A function that takes a thing and a list of optional-things, and
returns a thing'').
%
\hoogleplus then looks for Haskell programs that use library calls (from
a small, builtin set of functions) that satisfies the type signature.
%
Note that there may be an infinite number of so-called \emph{inhabitants} of a type.
%
This presents a search problem for users of the system.

How can a user sift through the programs synthesized to find the right
implementation of the type signature, for their use case?
%
We extend the system to provide some input-output examples for a chosen set of
queries, enough to run our study.
%
For now these examples were stubbed and chosen without particular regard for how
they might distinguish various candidate solutions.
%

>>>>

\section{Introduction}
Writing code is difficult and often inadvisable. 
%
A recent approach to this classic conundrum is \emph{program synthesis} which
takes a specification and generates a program that implements the
specification---saving us from ourselves by letting the computer do the work.
%
The specification may be a collection of input/output pairs
\cite{Feser_Chaudhuri_Dillig_2015}, a type signature \cite{hoogle_plus_2020},
or even a combination of the two \cite{Osera_Zdancewic_2015}.
%
These specifications are intentionally vague; many programs different
programs might meet the specification.
%
This keeps specification easy, but it requires the synthesizer to either guess,
or, more realistically, produce multiple candidate programs.

Sifting through a list of candidate programs can be timeconsuming, so much so
that it might be faster to write the code yourself.
%
If we could speed up this process, without requiring more input from the
user, we could allow programmers to both write easy specifications and
efficiently find their desired program.

In this work, we evaluate whether automatically generated input-output examples
for candidate programs will speed up the selection process.
%
We asked users to complete a series of synthesis tasks using a modified
version of, \hoogleplus, a program synthesizer for the Haskell
\cite{hoogle_plus_2020}, that produces input/output examples.
%
We find that while input/output examples do not appear to provide consisten
speedups, there is likely a set of circumstances where the speedup is
dramatic.
